Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-06-05 paper/paper.tex
caption 6

\begin{figure}
\centering
  \includegraphics[width=\textwidth]{posteriorCMD.png}
\caption{The expectation values of the posterior inferences (and error
  bars for a sub-sample). Notice that some parts of this \cmd\ are
  tighter than the prior, or noise-deconvolved \cmd. The visual of the
  prior is a sampling of the Gaussians, but this is the expectation
  value so this lies much closer to the center of the
  distribution. Similar to the toy model, where the pdf maximum of the
  noisier points lies in the center of the distribution.}
\label{fig:posteriorCMD}
\end{figure}

>>>>

\begin{figure}
\centering
  \includegraphics[width=\textwidth]{posteriorCMD.png}
\caption{The distribution of expectation values of the parallax posterior pdfs transformed into an absolute magnitude vs color, the \cmd, in the left panel, with the $1\sigma$ and $2\sigma$ contours of the distribution.
The right panel shows a subsample of data, plotting the expectation value and $1\sigma$ uncertainty of posterior pdf projected onto the \cmd.
Notice that some parts of this \cmd\ are tighter than the prior, or noise-deconvolved \cmd, shown in \figurename~\ref{fig:prior}
The visual of the prior is a sampling of the Gaussians, but this is the expectation
  value, so it lies much closer to the center of the
  distribution. Similar to the toy model, where the maximum of the
  posterior pdf of the noisy points lies closer to the center of the true distribution than the true values.}
\label{fig:posteriorCMD}
\end{figure}
